---
title: "Business Tracking"
author: "Susie Nguyen"
date: '2022-04-19'
output:  html_document
---

I analyzed my small business transactions to look for long-term trends on outgoing expenses by using R. My sample data set can be obtained at [my GitHub Repository](https://github.com/susieng/Business-Tracking-Projects).
In this project,I used ggplot2 to find out:

* Comparison of Different Order Types
* Most Purchased Categories 

## Setting up my environment
Notes: setting up my environment by loading the `tidyverse` and `plyr` packages:
```{r loading packages}
library(plyr)
library(tidyverse)
```

## Importing data set
Here we will go through a series of visualizations
```{r}
o <- read_csv('C:/Users/susie/OneDrive/Documents/Orders.csv')

head(o)
str(o)

o$date <- as.Date(o$Date, format = "%m/%d/%Y")
o$month <- as.Date(cut(o$date, breaks = "month"))

smr <- ddply(o, .(month, Type), summarise, cost = sum(Total), count = sum(Quantity))
smr <- smr[1:26,]
```

## Visualizing

### Comparison of Different Order Types
Here, we plot monthly expense of different order types
```{r}
ggplot(smr, aes(month, cost, col=Type)) +
  facet_wrap(~Type, ncol=2, scale="free_y") +
  geom_smooth(method="loess", se=F) + geom_point() +
  theme(axis.text.x=element_text(angle=45, hjust=1),
        legend.position="none") +
  labs(title="Comparison of Different Order Types",
       x="", y="Monthly total ($)")
```

### Most Purchased Categories
Here, we plot flipper length against body mass and look at the breakdown by species and sex
```{r}
yl <- ddply(smr, .(Type), summarise, m=mean(count))

ggplot(yl, aes(x=Type, y=m, fill = Type)) +
  geom_bar(stat="identity") +
  labs(y="Average monthly expense ($)", x="",
       title="Most Purchased Categories")
```

